\huge Tor's Usability for Censorship Circumvention

### 2016-04-19 pets2017-paper/pets2017-paper.tex
It was 3.5, not 4.0, when Tor Launcher was introduced.
Edits to intro and related work.

To our knowledge, this is the first user study investigating the usability of Tor as a 
censorship circumvention tool. We believe that this is a great opportunity for user research, both for investigating a case study of investigating the usability of a censorship circumvention tool, and also to help current Tor users censorship circumvention more easily. Not only will this allow for easier censorship circumvention, users who use tor will be provided with extra security features that other censorship circumvention tools do not provide, such as anonymity. Additionally, increasing the adoption of Tor as a censorship circumvention tool benefits other users who use Tor as an anonymity system by increasing the number of overall users on the Tor network~\cite{dingledine2006anonymity}.

Our study consists of two user studies set in three simulated censorship environments 
of varying levels of difficulty to circumvent. The mild, intermediate, and comprehensive 
environments required participants to connect, configure manually with default settings
and recommendations, and to configure manually without using defaults or recommendations. 
In both experiments, participants are informed that they are being censored, and that their 
goal is to reach a censored website by circumventing the censorship environment through
configuring Tor Browser.

The first user study is a small-scale, one-on-one experiment that collected 
behavioral patterns and failure cases with the interface through user observations
and interviews(Section~\ref{sec:qualitative}). This feedback was used to make changes to the interface (Section~\ref{redesign}). The second user study is a large-scale, data-centric user study
that collected data on user interactions with the interface to quantify the impact of the design changes (Section~\ref{quantitative}).

@@

\section{Related Work} 
There have been three published user studies on Tor. Clark et. al examined various deployment
options for Tor Browser, such as Vidalia, Privoxy, Torbutton, and Foxyproxy, and found that none of them 
were satisfactory from a usability perspective~\cite{clark2007usability}. Fabian et. al show that Tor's added
latency~\cite{dingledine2009performance} causes users
to be frustrated, cancel requests more often, and prevents user adoption~\cite{fabian2010privately}. 
Norcie et. al found found that 
64\% of users are unable to continue with installation or browsing at least once due to difficulties~\cite{norcie2012eliminating}.

There have been been no published usability evaluations of
Tor Browser since the 4.0 series, which introduced radical UI changes. 
The most recent usability effort is an unpublished pilot study  by Lee and Fifield~\cite {uxsprint} 
that tests the download, install, and  user interface of Tor Browser.  This study uncovered a number of issues~\cite{uxsprint2015-tickets}. Changes made are reflected in series 5.1 and later.

Previous user studies have not focused on specific features in isolation, while we choose to focus our study on 
the configuration interface. The configuration interface guides users through setting up network components required to circumvent censorship. 
This study examines that interface, and effectively, the usability of Tor as a censorship circumvention tool.

>>>>

To our knowledge, this is the first user study investigating the usability of Tor as a 
censorship circumvention tool. We believe that this is a great opportunity for user research, both for investigating a case study of investigating the usability of a censorship circumvention tool, and also to help current Tor users censorship circumvention more easily. Not only will this allow for easier censorship circumvention, users who use Tor will be provided with extra security features that other censorship circumvention tools do not provide, such as anonymity. Additionally, increasing the adoption of Tor as a censorship circumvention tool benefits other users who use Tor as an anonymity system by increasing the number of overall users on the Tor network~\cite{dingledine2006anonymity}.

Our study consists of two user studies set in three simulated environments
of mild to severe censorship.
Study participants had to circumvent censorship and access a blocked website
by configuring Tor Browser correctly.
The various levels of censorship required various levels of manual configuration,
ranging from almost none to detailed and specific settings.

The first user study is a small-scale, one-on-one experiment that collected 
behavioral patterns and failure cases with the interface through user observations
and interviews (Section~\ref{sec:qualitative}). This feedback was used to make changes to the interface (Section~\ref{redesign}). The second user study is a large-scale, data-centric user study
that collected data on user interactions with the interface to quantify the impact of the design changes (Section~\ref{sec:quantitative}).

@@

\section{Related Work} 
There have been three published user studies on Tor. Clark et~al.~\cite{clark2007usability} examined various deployment
options for Tor Browser, such as Vidalia, Privoxy, Torbutton, and Foxyproxy, and found that none of them 
were satisfactory from a usability perspective. Fabian et~al.~\cite{fabian2010privately} show that Tor's added
latency~\cite{dingledine2009performance} causes users
to be frustrated, cancel requests more often, and prevents user adoption. 
Norcie et~al.~\cite{norcie2012eliminating} found found that 
64\% of users are unable to continue with installation or browsing at least once due to difficulties.

There have been been no published usability evaluations of
Tor Browser since the 3.5 series, which introduced radical UI changes~\cite{torbrowser-35}.
The most recent usability effort is an unpublished pilot study by Lee and Fifield~\cite{uxsprint} 
that tested the downloading, installation, and browsing tasks in Tor Browser.  This study uncovered a number of issues~\cite{uxsprint2015-tickets},
some of which influenced changes in Tor Browser version~5.1 and later.

Previous user studies have been on the whole browsing experience,
without focusing on specific features in isolation.
We choose to focus our study on 
the browser's configuration interface, which guides users through setting up network components required to circumvent censorship. 
This study examines that interface with a focus on circumvention,
though we believe that this research and the changes we recommend
can be beneficial for non-circumventing users as well.
